Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-09-17 paper/case-study.tex
Fix minor typos

Within the software model, we have formalized some of the high-level requirements as assume-guarantee contracts.  We perform a formal analysis using the \agr\ to verify that the model satisfies the contracts.  For the initial version of our design, the verification passes.
%
Although we are satisfied with the results of the formal verification using AGREE, we have not yet analyzed the design for cyber-vulnerabilities.
In \brfcs, we analyze the model using one (or more) of the integrated cybersecurity analysis tools.
As the designers of the system, we reviewed the list of potential vulnerabilities, and then added new requirements to the system model.
%  To satisfy these requirements we need to mitigate the vulnerabilities discovered by the analysis by modifying the design.
%
For example, the vulnerbility analysis noted that UxAS as an open source project, so we marked that component as \texttt{uncontroled} (colored red in \figref{fig:sw-initial}) and added requirements for ensuring that unverified or malicious code (which could potentially be embedded in the component) is not able impact other components.

In total, we added seven cyber requirements from the vulnerability analysis into our model.  These include four \textit{wellformedness} requirements, two requirements for \textit{monitoring} the behavior of the open-source UxAS component, and an \textit{attestation} requirement for ensuring the Ground Station software has not been tampered with.  Requirements are imported into the model as goals in th assurance case \cite{resolute-destion}.  Because we can build the assurance case at any time during development, we can easily determine for a given snapshot of the model which requirements are not yet supported by evidence.

The intent of the \textit{wellformedness} requirements is to prevent
malformed messages from causing a buffer overrun or code injection
attack.  In the UAV design, such messages are most likely to originate
from a remote source or the uncontrolled UxAS component.  By placing
filters on the connections upstream of mission-critical components,
such attacks could be mitigated.  The Filter transform is therefore
applied for each wellformedness requirement, inserting filter
components on the incoming and outgoing UxAS connections.

@@

In addition to monitoring the UxAS output for malformed messages, we must also monitor for suspicious behavior.  This requires adding components for detecting that UxAS has crashed, as well as monitoring the correctness of the flight plans it produces.  The Monitor transform is applied for this class of mitigation.  We add a \textit{response} monitor to send an alert if UxAS does not emit a response within a set amount of time from receiving a request.  And we add a \textit{geofence} monitor to ensure that generated flight plans are compliant with the specified keep-in and keep-out zones.  The Geofence Monitor is a gated monitor in that it prevents the observed automation response from reaching the Waypoint Manager if the zones are violated.
The Geofence Monitor specification is shown in \figref{fig:geofence-monitor}.

@@

So far, we have addressed requirements that
%The requirements that have been addressed so far
mitigate vulnerabilities related to malformed messages and malicious behavior \textit{on-board} the UAV.  But we also want to protect against a compromised ground station transmitting well-formed, but malicious, commands. The final cyber requirement is mitigated by a transform that adds two components to the UAV software: an Attestation Manager for evaluating remote systems like the Ground Station, and an Attestation Gate for filtering messages from sources that have not been approved by the Attestation Manager~\cite{attestation-copland}.  The Attestation Manager \ckml\ implementation is automatically inserted into the application code base by \brfcs. The Attestation Gate does require a code contract that is completely generated by the transform since it has a very specialized behavior as defined by the transform.

After transforming the model to address the cyber requirements, the software architecture now appears as shown in \figref{fig:hardened-sw}.  The green shaded components were added by the transform with the exception of the UxAS component. The added components are critical for mitigating cyber attacks.
After unit testing the monitors, we formally verify the model with \agr\ to show that all of the component contracts are satisfied.
We then run \splt\ to produce provably-correct code.
The synthesized code is output to a directory in the build file system with the location specified for each component in the model.  The corresponding correctness proof is used in our assurance case as additional evidence that the vulnerability has been properly mitigated.

@@

\paragraph{UxAS vulnerability exploit} Line Search Tasks with greater than 90 waypoints were transmitted from the Ground Station, triggering a vulnerability that crashes UxAS.   When this occurs, UxAS is unable to generate an Automation Response.
This vulnerability is mitigated by inserting a Response Monitor that checks to see if UxAS outputs an Automation Response message shortly after receiving an Automation Request.  For this scenario, we chose for the monitor to output a status message, which would then be received by the Ground Station and an appropriate action taken.

>>>>

Within the software model, we have formalized some of the high-level requirements as assume-guarantee contracts.  We perform a formal analysis with \agr\ to verify that the model satisfies the contracts.  For the initial version of our design, the verification passes.
%
Although we are satisfied with the results of the formal verification using AGREE, we have not yet analyzed the design for cyber-vulnerabilities.

In \brfcs, we analyze the model using one (or more) of the integrated cybersecurity analysis tools.
As the designers of the system, we reviewed the list of potential vulnerabilities, and then added new requirements to the system model.
%  To satisfy these requirements we need to mitigate the vulnerabilities discovered by the analysis by modifying the design.
%
For example, the vulnerbility analysis noted that UxAS is an open source project, so we marked that component as \texttt{uncontroled} (colored red in \figref{fig:sw-initial}) and added requirements for ensuring that unverified or malicious code (which could potentially be embedded in the component) is not able impact other components.

In total, we added seven cyber requirements from the vulnerability analysis into our model.  These include four wellformedness requirements on data, two requirements for monitoring the behavior of the open-source UxAS component, and an attestation requirement for ensuring the Ground Station software has not been tampered with.  Requirements are imported into the model as goals in the assurance case.  Because we can build the assurance case at any time during development, we can easily determine for a given snapshot of the model which requirements are not yet supported by evidence.

The intent of the wellformedness requirements is to prevent
malformed messages from causing a buffer overrun or code injection
attack.  In the UAV design, such messages are most likely to originate
from a remote source or the uncontrolled UxAS component.  By placing
filters on the connections upstream of mission-critical components,
such attacks could be mitigated.  The Filter transform is therefore
applied for each wellformedness requirement, inserting filter
components on the incoming and outgoing UxAS connections.

@@

In addition to monitoring the UxAS output for malformed messages, we must also monitor for suspicious behavior.  This requires adding components for detecting that UxAS has crashed, as well as monitoring the correctness of the flight plans it produces.  The Monitor transform is applied for this class of mitigation.  We add a \textit{response} monitor to send an alert if UxAS does not emit a response within a set amount of time from receiving a request.  And we add a \textit{geofence} monitor to ensure that generated flight plans are compliant with the specified keep-in and keep-out zones.  The Geofence Monitor is a gated monitor in that it prevents the observed automation response from reaching the Waypoint Manager if the zones are violated.
The Geofence Monitor code contract is shown in \figref{fig:geofence-monitor}.

@@

So far, we have addressed requirements that
%The requirements that have been addressed so far
mitigate vulnerabilities related to malformed messages and malicious behavior \textit{on-board} the UAV.  But we also want to protect against a compromised ground station transmitting well-formed, but malicious, commands. The final cyber requirement is mitigated by a transform that adds two components to the UAV software: an Attestation Manager for evaluating remote systems like the Ground Station, and an Attestation Gate for filtering messages from sources that have not been approved by the Attestation Manager.  The Attestation Manager \ckml\ implementation is automatically inserted into the application code base by \brfcs. The code contract for the Attestation Gate is completely generated by the transform since its behavior is specific to attestation.

After transforming the model to address the cyber requirements, the software architecture now appears as shown in \figref{fig:hardened-sw}.  The shaded components (green) were added by the transform with the exception of the UxAS component (red).

After unit testing the monitors, we formally verify the model with \agr\ to show that all of the component contracts are satisfied.
We then run \splt\ to produce provably-correct code.
The synthesized code is output to a directory in the build file system with the location specified for each component in the model.  The corresponding correctness proof is used in our assurance case as additional evidence that the vulnerability has been properly mitigated.

@@

\paragraph{UxAS vulnerability exploit} Line Search Tasks with greater than 90 waypoints were transmitted from the Ground Station, triggering a vulnerability that crashes UxAS.   When this occurs, UxAS is unable to generate an Automation Response. The response monitor detected and signaled the Ground Station when UxAS failed to respond to the request.

### 2022-09-17 paper/high-assurance-contracts.tex
Fix minor typos

Generally, AGREE contracts do not describe the computation that a
component performs. This is entirely by design: AGREE is intended to
reason about component behavior solely at the specification
level. However, the syntax of AGREE provides enough expressiveness to
support the notion of a \emph{code contract}: a contract from which an
implementation can be extracted. First we must discuss a class of
guarantees---\emph{output guarantees}---which determine the values on
all output ports of a component.

@@

\subsubsection*{Imperative code contracts.}
\egm{Remove.
Replace with the informal presentation of temporal squashing \emph{or} remove entirely.}

@@

As previously discussed, transformations carried out in the BriefCASE
interface have created a cyber-hardened system, protecting against
malicious AI behavior by the insertion of a high-assurance filter and
monitor between the AI and the WM (see \figref{fig:hardened}). The
filter protects the WM from malformed data and the monitor protects
the WM from (possibly malicious) spontaneous or delayed responses.
These components were added, one at a time, by
\begin{enumerate}
  \item selecting the connection in the model where the
    component is to appear,
  \item choosing the appropriate transformation, and
  \item specifying the relevant filtering or monitoring \emph{policy} (behavior).
\end{enumerate}

%% The system designer provides configuration parameters for the
%% transformation in a dialogue box.  The dialogue box for adding a
%% filter is shown in \figref{fig:dialogue}.  All high-assurance
%% components rely on a \emph{policy} to define behavior as seen in the
%% last field of the dialogue box.  A filter policy defines well-formed
%% data while a monitor policy defines an invariant over inputs and
%% outputs.  These policies can be stated directly in the wizard, or they
%% can be left blank and added later to the AGREE contract generated by
%% the transformation.

BriefCASE creates all the needed AADL for the new high-assurance
component, and its connections in the system implementation, as part
of the transformation.  It also creates a default code contract with
appropriate output guarantees leaving only the component behavior
(policy) to be specified.

@@

\subsubsection{Monitor specification}

>>>>

Generally, AGREE contracts do not describe the computation that a
component performs. This is entirely by design: AGREE is intended to be declarative and
reason about component behavior solely at the specification
level. It defines what a component computes and not how it computes it. However, the syntax of AGREE provides enough expressiveness to
support the notion of a \emph{code contract}: a contract from which an
implementation can be extracted. First we must discuss a class of
guarantees---\emph{output guarantees}---which determine the values on
all output ports of a component.

@@

\subsubsection*{Imperative code contracts.}

@@

@@

### 2022-09-17 paper/overview.tex
Fix minor typos

\brfcs\ integrates additional tools into OSATE to analyze, identify, and address cybersecurity vulnerabilities in the baseline model (top of \figref{fig:tool-arch}).
\brfcs\ provides access to analysis tools that examine the model, report potential cyber vulnerabilities,
and suggest requirements for mitigation \cite{dcrypps2019,gearcase2020}.
Designers add these requirements to the \brfcs\ project requirements repository. 
A key part of the requirements management in \brfcs\ is a corresponding assurance case that provides evidence, computed directly from the model or by supporting analysis tools, showing how each requirement is satisfied.
Evidential statements must exist to address the added cyber requirements in order for \brfcs\ to build the assurance case for the project.

\brfcs\ provides an extendable library of model transformations to address requirements for common cyber vulnerabilities:
\begin{compactitem}
	\item \textbf{Filter}: block messages that do not conform to a given specification
	\item \textbf{Monitor}: detect and alert violations at runtime
	\item \textbf{Gate}: block messages in the presence of an alert
	\item \textbf{Attestation}: measure non-local software to assess trustworthiness
	\item \textbf{Virtualization}: isolate components
	\item \textbf{Proxy}: enable HTTPS message inspection 
	\item \textbf{seL4}: transform component definitions for the seL4 secure micro kernel
\end{compactitem}
Transformations update the model's architecture with new components and the assurance case with new required evidential statements.

@@

The contributions discussed in this manuscript relate to the aspects of \brfcs\ concerning evidence that a high-assurance component meets its intended purpose and is properly implemented.
This manuscript defines a \emph{code contract} language that is a subset of the \agr\ language with sequential evaluation semantics as opposed to the existing parallel semantics of \agr.
The sequential semantics are requisite to code synthesis and are defined such that \agr\ is able to still prove consistency in the contract composition of the model.

This manuscript further defines a stylized \emph{test contract} for unit testing code contracts outside of the system composition to verify input to output behavior as well as general properties of the code contract.
As such, the behavior of a high assurance component is defined by the designer in a code contract, and then using the existing \agr\ model checker, test contracts prove the desired code contract behavior.
Once the designer is satisfied that the code contract is correct, the system composition is verified to conclude that the contract meets its intended purpose.

Showing that a component is properly implemented is accomplished through formal synthesis from the code contract (bottom of \figref{fig:tool-arch}).
This manuscript presents the Semantic Properties of Language and Automata Theory (\splt) tool that generates \emph{\ckml} code to implement the code contract.
\ckml\ is a functional language that includes additional proofs and tools built around it \cite{cakeml}.
The \ckml\ compiler itself is verified to generate binary implementations that are equivalent in semantics to the original input program.
That proof ensures that the resulting binary exactly preserves the meaning of the original code contract and assures that the component is properly implemented.

>>>>

\brfcs\ integrates additional tools into OSATE to analyze, identify, and address cybersecurity vulnerabilities in the baseline model (top of \figref{fig:tool-arch}).
\brfcs\ provides access to analysis tools that examine the model, report potential cyber vulnerabilities,
and suggest requirements for mitigation \cite{dcrypps2019,gearcase2020}.
Designers add these requirements to the \brfcs\ project requirements repository. 
A key part of the requirements management in \brfcs\ is a corresponding assurance case that provides evidence, computed directly from the model or by supporting analysis tools, showing how each requirement is satisfied.
Evidential statements must exist to address the added cyber requirements in order for \brfcs\ to build the assurance case for the project \cite{resolute-destion}.

\brfcs\ provides an extendable library of model transformations to address requirements for common cyber vulnerabilities:
\begin{compactitem}
	\item \textbf{Filter}: block messages that do not conform to a given specification
	\item \textbf{Monitor}: detect and alert violations at runtime
	\item \textbf{Gate}: block messages in the presence of an alert
	\item \textbf{Attestation}: measure non-local software to assess trustworthiness \cite{attestation-copland}
	\item \textbf{Virtualization}: isolate components
	\item \textbf{Proxy}: enable HTTPS message inspection 
	\item \textbf{seL4}: transform component definitions for the seL4 secure micro kernel
\end{compactitem}
Transformations update the model's architecture with new components and the assurance case with new required evidential statements.

@@

The contributions discussed in this paper relate to the aspects of \brfcs\ concerning evidence that a high-assurance component meets its intended purpose and is properly implemented.
This paper defines a \emph{code contract} language that is a subset of the \agr\ language with sequential evaluation semantics as opposed to the existing parallel semantics of \agr.
The sequential semantics are requisite to code synthesis and are defined such that \agr\ is able to still prove consistency in the contract composition of the model.

This paper further defines a stylized \emph{test contract} for unit testing code contracts outside of the system composition to verify input to output behavior as well as general properties of the code contract.
As such, the behavior of a high assurance component is defined by the designer in a code contract, and then using the existing \agr\ model checker, test contracts prove the desired code contract behavior.
Once the designer is satisfied that the code contract is correct, the system composition is verified to conclude that the contract meets its intended purpose.

Showing that a component is properly implemented is accomplished through formal synthesis from the code contract (bottom of \figref{fig:tool-arch}).
This paper presents the Semantic Properties of Language and Automata Theory (\splt) tool that generates \emph{\ckml} code to implement the code contract.
\ckml\ is a functional language that includes additional proofs and tools built around it \cite{cakeml}.
The \ckml\ compiler itself is verified to generate binary implementations that are equivalent in semantics to the original input program.
That proof ensures that the resulting binary exactly preserves the meaning of the original code contract and assures that the component is properly implemented.

### 2022-09-17 paper/related-work.tex
Fix minor typos

%% DO NOT REMOVE --- BUT FEEL FREE TO REVISE
%% Specifically requested by the reviewers to be included in this paper!!!
Another model based approach to secure system architectures follows a pattern similar to \brfcs\ by inserting pre-verified components into the architecture to give certain guarantees \cite{6209212}.
In that work, the data connections are annotated with security properties as are the components.
A secondary analysis determines if the components meet the security requirements of the data connections, and if not, inserts new security enhancing components in the connection.
The insertion algorithm considers time cost when inserting components to preserve worst-case execution times mandated by the system.
\brfcs\ has the ability to insert pre-verified components based on cyber-requirements, but does not currently have the ability to annotate connections with security properties or automatically infer where secure components need to be inserted.

Assume-guarantee reasoning for compositional verification in reactive systems is well-studied \cite{10.1007/978-3-642-28891-3_13, 10.1145/2658982.2527272, 10.1007/978-3-319-17524-9_7}.
The first steps toward synthesis of leaf-component contracts determined if leaf-component contracts are realizable \cite{10.1007/978-3-319-17524-9_13, 10.1007/978-3-319-29613-5_7}.
These led to algorithms for component synthesis from Lustre models based on realizability \cite{katis2017synthesis, 10.1007/978-3-319-89963-3_10}.
The algorithms discover a transition relation that preserve the contract guarantees under all allowed inputs and can be directly transformed into the language intended for the system's implementation.
Two such algorithms are implemented in the \agr\ verification engine \cite{jkind}.
These synthesis algorithms take in a declarative specification that states \emph{what is to be computed}, and then they have to infer \emph{how to compute it} for the implementation.
Code contracts are imperative, by design, so the designer specifies directly how the computation of the high-assurance component takes place thereby avoiding the question of realizability entirely.
That said, the test contracts in this paper can be declarative, stating what is to be computed, if desired, and \agr\ can then prove if the code contracts accomplishe that.

>>>>

%% DO NOT REMOVE --- BUT FEEL FREE TO REVISE
%% Specifically requested by the reviewers to be included in this paper!!!
Another model based approach to secure system architectures follows a pattern similar to \brfcs\ with attestation by inserting pre-verified components into the architecture to give certain guarantees \cite{6209212}.
In that work, the data connections are annotated with security properties as are the components.
A secondary analysis determines if the components meet the security requirements of the data connections, and if not, inserts new security enhancing components in the connection.
The insertion algorithm considers time cost when inserting components to preserve worst-case execution times mandated by the system.
\brfcs\ has the ability to insert pre-verified components based on cyber-requirements, but does not currently have the ability to annotate connections with security properties or automatically infer where secure components need to be inserted.

Assume-guarantee reasoning for compositional verification in reactive systems is well-studied \cite{10.1007/978-3-642-28891-3_13, 10.1145/2658982.2527272, 10.1007/978-3-319-17524-9_7}.
The first steps toward synthesis of leaf-component contracts determined if leaf-component contracts are realizable \cite{10.1007/978-3-319-17524-9_13, 10.1007/978-3-319-29613-5_7}.
These led to algorithms for component synthesis from Lustre models based on realizability \cite{katis2017synthesis, 10.1007/978-3-319-89963-3_10}.
The algorithms discover a transition relation that preserves the contract guarantees under all allowed inputs and can be directly transformed into the language intended for the system's implementation.
Two such algorithms are implemented in the \agr\ verification engine \cite{jkind}.
These synthesis algorithms take in a declarative specification that states \emph{what is to be computed}, and then they have to infer \emph{how to compute it} for the implementation.
Code contracts are imperative, by design, so the designer specifies directly how the computation of the high-assurance component takes place thereby avoiding the question of realizability entirely.
That said, the test contracts in this paper can be declarative, stating what is to be computed, if desired, and \agr\ can then prove if the code contracts accomplishe that.

### 2022-09-17 paper/synthesis.tex
Remove filter alerts sentence
Fix minor typos

Synthesis maps from model and specifications to code. The SPLAT tool
traverses the system architecture looking for occurrences of high
assurance components specified by code contracts; for each such
occurrence it generates a CakeML program. SPLAT supports three kinds
of behavioral specification from which to generate code. In increasing
order of expressiveness, these are: regular expressions, contiguity
types, and AGREE specifications. In earlier work we have described how
regular expressions and contiguity types are used as specification
languages for verified filter implementations. In the present paper,
we extend this \emph{specification oriented} approach to the
Turing-complete specifications of AGREE.  We give a short review of
that previous work before going into detail on AGREE.

@@

The contiguity type specification and wellformedness predicate for
the filter are shown in \figref{fig:filter-spec} and the synthesized
CakeML code is in \figref{fig:filter-cakeml}. The code is called at
dispatch by the scheduler. The \texttt{API.callFFI} is the link to the
communication fabric to capture input and provide output. The body of
the function restates the filter contract to make the appropriate
assignments in a way that matches the truth value of the predicate in
the filter guarantee.  The auto-generated AGREE specification raises
an alert output when the relation is violated.

>>>>

Synthesis maps from model and specifications to code. The SPLAT tool
traverses the system architecture looking for occurrences of high
assurance components specified by code contracts; for each such
occurrence it generates a CakeML program. SPLAT supports three kinds
of behavioral specification from which to generate code. In increasing
order of expressiveness, these are: regular expressions, contiguity
types, and code contracts. In earlier work we have described how
regular expressions and contiguity types are used as specification
languages for verified filter implementations. In the present paper,
we extend this \emph{specification oriented} approach to the
Turing-complete specifications of code contracts in \agr.  We give a short review of
that previous work before going into detail on the synthesis.

@@

The contiguity type specification and wellformedness predicate for
the filter are shown in \figref{fig:filter-spec} and the synthesized
CakeML code is in \figref{fig:filter-cakeml}. The code is called at
dispatch by the scheduler. The \texttt{API.callFFI} is the link to the
communication fabric to capture input and provide output. The body of
the function restates the filter contract to make the appropriate
assignments in a way that matches the truth value of the predicate in
the filter guarantee.

### 2022-09-17 paper/testing.tex
Fix minor typos

We have observed three common types of mistakes in code contracts (aside from self-consistency, which is
already checked): vacuity, under-specification, and missed corner cases.
Vacuity is a common pitfall with implication when the left hand side is always false, making the implication true. 
Under-specification is very challenging, as \agr\ is not able to prove anything (or it can prove everything in the case of existential properties), so nothing is actually known after verification except that the contract is under-specified. 
Missed corner cases is a common problem to all disciplines.
It is an especially difficult challenge here because there is no direct to exercise code contracts (e.g., there is no runtime \emph{per se}).

A tempting approach to exercising code contracts directly is to use \splt\ to create the target binary and then use that runtime with with traditional testing.
Such an approach adds extra steps, including test harneses, that are not needed, as it is
possible to bridge the formal model in \agr, with its proof system, to
traditional validation using tests.
The intuition for that bridge comes from the compositional reasoning in AADL and \agr. 
Effectively, a code contract for a high assurance component should be a valid implementation of a test scenario.
In other words, the test scenario, as expressed in a test contract, is the desired behavior of the system, and the code contract implements that behavior.

A test contract defines the test scenario for the code contract to implement.
It does this by assuming the test input and guarantying the test output akin to a unit test. 
The code contract implementation (e.g., the subject under test).
The \agr\ analysis then proves if the code contract, given the test inputs, is strong enough to prove the test contract outputs.
Here the test contract assumptions strengthen the code contract assumptions to a single input, and the test contract guarantees weaken, or leave unchanged, the code contract output for that test input, depending on the goal of the test.
In other words, according to Liskov substitution, \agr\ proves if the code contract is a safe substitution for the test contract.

@@

\figref{fig:test} is a unit test, with its test contract, for the monitor in \figref{fig:hardened}.
The test contract checks if the monitor output coincides with the response that comes one step after the request.
It also checks that the alarm is not output.
\begin{compactitem}
\item \lineref{line:tst-index}: An index to use to define the test input and expected test output through time.
\item \lineref{line:tst-assume-1} and \lineref{line:tst-assume-2}: The test input. These define when the request and response message events should appear relative to the index.
\item \lineref{line:tst-guarantee-1} and \lineref{line:tst-guarantee-2}: The expected test output. 
The test additionally proves that nothing happens after the initial test input and expected output, \ie, no more input is provided and no more output is generated.
\item \linesref{line:tst-imp-start}{line:tst-imp-end}: The implementation with the component under test (\lineref{line:tst-imp-comp}).
\end{compactitem}
\figref{fig:test-output} is the \agr\ output for the test, showing that it passes.

Test contracts are effective in detecting vacuity, under-specified behavior, and missed corner cases.
They enables designers to iteratively develop code contracts inside OSATE with \agr, and they build assurance that the code contract reflects the desired behavior with black-box, white-box, and other test coverage metrics.
These same tests can be synthesized to the backend implementation for traditional testing if for example, the code contract is a model of an existing legacy binary.

>>>>

We have observed three common types of mistakes in code contracts (aside from self-consistency, which is
already checked): vacuity, under-specification, and missed corner cases.
Vacuity is a common pitfall with implication when the left hand side is always false, making the implication true. 
Under-specification is very challenging, as \agr\ is not able to prove anything (or it can prove everything in the case of existential properties), so nothing is actually known after verification except that the contract is under-specified. 
Missed corner cases is a common problem to all disciplines.
It is an especially difficult challenge here because there is no direct way to exercise code contracts, \eg, there is no runtime \emph{per se}.

A tempting approach to exercising code contracts directly is to use \splt\ to create the target binary and then use that runtime with traditional testing.
Such an approach adds extra steps, including test harneses, that are not needed, as it is
possible to bridge the formal model in \agr, with its proof system, to
traditional validation using tests.
The intuition for that bridge comes from the compositional reasoning in AADL and \agr. 
Effectively, a code contract for a high assurance component should be a valid implementation of a test scenario.
In other words, the test scenario, as expressed in a test contract, is the desired behavior of the system, and the code contract implements that behavior.

A test contract defines the test scenario for the code contract to implement.
It does this by assuming the test input and guarantying the test output akin to a unit test. 
The code contract is used as the implementation, \eg, it is the test subject.
The \agr\ analysis then proves if the code contract, given the test inputs, is strong enough to prove the test contract outputs.
Here the test contract assumptions strengthen the code contract assumptions to a single input, and the test contract guarantees weaken, or leave unchanged, the code contract output for that test input, depending on the goal of the test.
In other words, according to Liskov substitution, \agr\ proves if the code contract is a safe substitution for the test contract.

@@

\figref{fig:test} is a unit test, with its test contract, for the monitor in \figref{fig:hardened}.
The test contract checks if the monitor output coincides with the response that comes one step after the request.
It also checks that the alarm is not output.
\begin{compactitem}
\item \lineref{line:tst-index}: An index to use to define the test input and expected test output through time.
\item \lineref{line:tst-assume-1} and \lineref{line:tst-assume-2}: The test input. These define when the request and response message events should appear relative to the index.
\item \lineref{line:tst-guarantee-1} and \lineref{line:tst-guarantee-2}: The expected test output. 
The test additionally proves that nothing happens after the initial test input and expected output, \ie, no more input is provided and no more output is generated.
\item \linesref{line:tst-imp-start}{line:tst-imp-end}: The implementation with the component under test (\lineref{line:tst-imp-comp}).
\end{compactitem}
\figref{fig:hardened-certificate}(a) is the \agr\ output for the test showing that it passes.

Test contracts are effective in detecting vacuity, under-specified behavior, and missed corner cases.
They enable designers to iteratively develop code contracts inside OSATE with \agr, and they build assurance that the code contract computes the desired behavior with black-box, white-box, and other test coverage metrics.
These same tests can be synthesized to the backend implementation for traditional testing, if for example, the code contract is a model of an existing legacy binary.
